---
title: "new gather"
author: "Tonnu"
date: "11/14/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
  # Libraries I'll need
library(tidyverse)
library(purrr)
library(dplyr)
library(janitor)
library(readxl)
library(maptools)
library(leaflet)
library(sf)
library(sp)
library(ggplot2)
library(rgdal)
library(grid)
library(wbstats)
```

1. Cleaning

```{r read_dams}

 # Create function to import GRandD dams and reservoirs data. 

read_dams <- function(file, region){
  
  # Specify columns, clean names, deselect problematic variable. 
  
  read_excel(file, sheet = "Dams", skip = 1, col_types = c("text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "numeric", 
        "numeric", "numeric", "numeric", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "numeric", 
        "numeric", "text", "text", "text")) %>%
  clean_names() %>%
  select(-other_reference_s) %>%
    
    # Create variable region, since datasets are for individual regions. 
    
  mutate(region = region) 
}

clean_dams <- function(df){
  
  # Clean up dam purpose columns. 
  
  df_2 <- df %>%
  select(name_of_dam, irrigation:other) %>%
  pivot_longer(cols = c(irrigation:other), names_to = "purpose", values_to = "value") %>%
  drop_na(value) %>%
  group_by(name_of_dam, value) %>%
  mutate(purpose = list(purpose)) %>%
  mutate(multipurpose = n()) %>%
  mutate(multipurpose = ifelse(multipurpose > 1, "yes", "no")) %>%
  ungroup() %>%
  select(-value)
  
  # Remove duplicates with this line of code.
  
  df_2 <- df_2[!duplicated(df_2), ]
  
  # Join final cleaned data.
  
  df %>%
    select(-(irrigation:other)) %>%
  left_join(df_2, by = "name_of_dam")
}

import_dams <- function(file, region){
  read_dams(file, region) %>%
  clean_dams()
} # Final function

 # Import GRandD data for each world region. 

south_america <- import_dams("raw_data/dams/soamer_aquastat.xlsx", "South America")
central_america <- import_dams("raw_data/dams/cenamer_aquastat.xlsx", "Central America")
north_america <- import_dams("raw_data/dams/namer_aquastat.xlsx", "North America")
europe <- import_dams("raw_data/dams/europe_aquastat.xlsx", "Europe") 
africa <- import_dams("raw_data/dams/africa_aquastat.xlsx", "Africa")
middle_east <- import_dams("raw_data/dams/midest_aquastat.xlsx", "Middle East")
central_asia <- import_dams("raw_data/dams/casia_aquastat.xlsx", "Central Asia")
east_asia <- import_dams("raw_data/dams/seasia_aquastat.xlsx", "East Asia") %>%
  filter(country %in% c("China", "Japan", "Korea", "Democratic People's Republic of Korea", "Republic of Korea", "Mongolia"))
south_asia <- import_dams("raw_data/dams/seasia_aquastat.xlsx", "South Asia") %>%
  filter(country %in% c("India", "Bangladesh", "Pakistan", "Sri Lanka", "Bhutan", "Nepal")) 
se_asia <- import_dams("raw_data/dams/seasia_aquastat.xlsx", "South East Asia") %>%
  filter(!country %in% c("China", "Japan", "Korea", "Democratic People's Republic of Korea", "Republic of Korea", "India", "Bangladesh", "Pakistan", "Sri Lanka", "Bhutan", "Nepal", "Mongolia"))
oceania <- import_dams("raw_data/dams/oceania_aquastat.xlsx", "Oceania")

  # Simplified for about page

asia <- import_dams("raw_data/dams/seasia_aquastat.xlsx", "Asia") %>%
  bind_rows(central_asia) %>%
  mutate(region = "Asia")
central_south <- bind_rows(south_america, central_america) %>%
  mutate(region = "Central and South America")

  # Bind rows and save as .rds file for all dams. 

all_dams <- bind_rows(south_america, central_america, north_america, europe, africa, middle_east, central_asia, east_asia, south_asia, se_asia, oceania)

all_dams_about <- bind_rows(central_south, north_america, europe, africa, middle_east,
                            asia, oceania)

saveRDS(all_dams, "shiny_app/all_dams.rds")
saveRDS(all_dams_about, "shiny_app/all_dams_about.rds")
```
```{r wbstats}

wb_import <- function(indicator, name){
  wb_data(indicator = indicator, start_date = 1900, end_date = 2015) %>%
  select(code = iso3c, date, name = indicator) %>%
  mutate(date = as.double(date))
}

# Import World Bank population data. 

pop <- wb_import(indicator = "SP.POP.TOTL", name = pop)

# Import World Bank GDP data. 

gdp <- wb_import(indicator = "NY.GDP.MKTP.CD", name = gdp)

# Import World Bank water availability data. 

safe_water <- wb_import(indicator = "SH.H2O.SMDW.ZS", name = water_avail)

# Import World Bank water withdrawal data data. 

water_withdraw <- wb_import(indicator = "ER.H2O.FWTL.ZS", name = water_withdraw)

# Import World Bank agricultural land data. 

ag_land <- wb_import(indicator = "AG.LND.AGRI.ZS", name = ag_land)

# Import World Bank agricultural irrigated land data. 

ir_land <- wb_import(indicator = "AG.LND.IRIG.AG.ZS", name = ir_land_percent)

# Join and save as .rds for all WB stats. 

all_wbstats <- list(pop, gdp, water_avail, water_withdraw, ag_land, ir_land_percent) %>% 
  reduce(left_join, by = c("code", "date")) %>%
  rename(pop = name.x,
         gdp = name.y,
         safe_water = name.x.x,
         water_withdraw = name.y.y,
         ar_land = name.x.x.x,
         ir_land = name.y.y.y)

saveRDS(all_wbstats, "shiny_app/all_wbstats.rds")
```
```{r read_other}
subnational <- read_excel("raw_data/subnational/clean_formatted_wb_subnational.xlsx")


```
```{r save_rds}
file_path <- tibble(country_name = c("Argentina", "Bolivia", "Brazil", "Burkina Faso",
                                    "China", "Cuba", "India", "Indonesia", 
                                    "Iran", "Laos", "Mexico", "Romania", "Russia", 
                                    "South Africa", "Turkey", "Uruguay", 
                                    "Zimbabwe"),
                   file_path = c("raw_data/subnational/geometry/argentina/geo1_ar2010.shp",
                   "raw_data/subnational/geometry/bolivia/geo1_bo2012.shp",
                   "raw_data/subnational/geometry/brazil/geo1_br2010.shp",
                   "raw_data/subnational/geometry/burkina_faso/geo1_bf2006.shp",
                   "raw_data/subnational/geometry/china/geo1_cn2000.shp",
                   "raw_data/subnational/geometry/cuba/geo1_cu2012.shp",
                   "raw_data/subnational/geometry/india/geo1_id2010.shp",
                   "raw_data/subnational/geometry/indonesia/geo1_in2009.shp",
                   "raw_data/subnational/geometry/iran/geo1_ir2011.shp",
                   "raw_data/subnational/geometry/laos/geo1_la2005.shp",
                   "raw_data/subnational/geometry/mexico/geo1_mx2015.shp",
                   "raw_data/subnational/geometry/romania/geo1_ro2011.shp",
                   "raw_data/subnational/geometry/russia/geo1_ru2010.shp",
                   "raw_data/subnational/geometry/south_africa/geo1_za2016.shp",
                   "raw_data/subnational/geometry/turkey/geo1_tr2000.shp",
                   "raw_data/subnational/geometry/uruguay/geo1_uy2011.shp",
                   "raw_data/subnational/geometry/zimbabwe/geo1_zw2012.shp"
                   ))
  
saveRDS(file_path, "shiny_app/file_path.rds")


```



2. Maps

```{r dams}
  dam_num <- all_dams %>%
  drop_na(decimal_degree_latitude) %>%
  group_by(country, region) %>%
  summarize(dam_numbers_country = n(), .groups = "drop")  %>%
  arrange(desc(dam_numbers_country)) %>%
  slice(1:20)
  
  dam_num %>% slice(1:10) %>%
    ggplot(aes(country, dam_numbers_country, fill = region)) + 
  geom_col() +
    theme(axis.text.x = element_text(angle = 90)) 
  
  all_dams_about <- readRDS("shiny_app/all_dams_about.rds") 

  
    all_dams_about %>% 
      group_by(region) %>%
      drop_na(completed_operational_since) %>%
      mutate(count = n()) %>%
    ggplot(aes(completed_operational_since, fill = fct_reorder(region, count))) + 
 geom_bar(position = "stack") + 
      theme(axis.text.x = element_text(angle = 90)) + 
      scale_fill_discrete(name = "Regions") +
      scale_x_discrete(breaks = c(seq(from = 0, to = 2019, by = 50))) + 
      theme_light()

all_dams %>% 
      filter(ISO3 == "VNM", major_basin == "Red") %>%
      group_by(completed_operational_since) %>%
      #drop_na(completed_operational_since) %>%
      #summarize(count = n(), .groups = "drop") 
      
    ggplot(aes(completed_operational_since)) + 
  geom_bar() + 
      theme(axis.text.x = element_text(angle = 90)) 
    
    unique(all_dams$region)
    
      em_dat <- read_excel("raw_data/emdat_public_2020_11_01_query_uid-MSWGVQ.xlsx",
                       skip = 6) %>%
    clean_names()
  
```
my_simpl <- wrld_simpl 

my_simpl@data <- left_join(dam_numbers, wrld_simpl@data, by = "ISO3", na.rm = TRUE, 
                           c)

type_convert(
  wrld_simpl@data,
  col_types = "numeric",
  na = c("", "NA"),
  trim_ws = TRUE,
  locale = default_locale()
)

cols(my_simpl@data$dam_numbers = col_double())

#na_simpl@polygons <- na_simpl@polygons %>%
 # filter(ID %in% c("CAN", "MEX", "USA"))
  
#have all the data for all the continents --> replace na_simpl = wrld_simpl 

pal <- colorNumeric(
  palette = "YlGnBu",
  domain = my_simpl@data$dam_numbers
)

leaflet() %>% 
  setView(lng = 0, lat = 0, zoom = 0) %>%
  addTiles() %>%
  addPolygons(stroke = FALSE, smoothFactor = 0.2, fillOpacity = 1,
    color = ~pal(dam_numbers)) %>%
  addLegend("bottomright", pal = pal, values = ~ dam_numbers,
    title = "Dam numbers",
    labFormat = labelFormat(prefix = "$"),
    opacity = 1)
  
```{r test}
  leaflet() %>%
  addTiles() %>%
  addCircleMarkers(data = all_dams, lat = ~ decimal_degree_latitude, lng = ~ decimal_degree_longitude, radius = 0.1) %>%
  setView(lat = 0, lng = 0, zoom = 2)
```
  
  
  
  
  
  
  
  
  
  
  (PL: 
  In this project, I'm going to create maps of at least 5 
                   major river delta and their basin in Asia (the Irrawaddy, 
                   the Mekong, the Red, the Yellow, the Yangtze, the 
                   Brahmaputra-Ganges, etc), looking at hydrological control 
                   infrastructure in the basin, such as river dikes and large 
                   dams, and compare it against water-related disaster events, 
                   such as drought, flood, famine, over time.
  I'm also interested in population distribution, land use, 
                     and topography of each basin. The goal is to illustrate how 
                     Asia's most powerful rivers are being managed, their 
efficacy and problems over time, and the population most 
vulnerable to these decisions. Furthermore, is there a 
sacficice zone identifiable in these basins? That's 
                     something I hope to be able to shed light on.
  
  Right now I'm looking at data from the Emergency 
                     Events Database (EM-DAT), but I'm also looking at 
government census for population data. Geographic studies 
are a good place to figure out the area of delta and 
topographic information. The most difficult thing is 
records of disasters, these tend to be all over the place, 
but I think a good place to start is in comprehensive 
environmental histories of a river delta, such as 
David Pietz's book on the Yellow River, Chris Courtney's 
book on the Yangtze river and the historic 1931 flood, or 
Arupjyoti Saikia's comprehensive work on the Brahmaputra 
                     river delta.)
