```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(sf)
library(tidyverse)
library(dplyr)
library(leaflet)
library(ggplot2)
library(wbstats)
library(janitor)
library(sp)
library(rgdal)
library(rgeos)
library(grid)
library(readxl)
library(maptools)

all_dams <- read_rds("shiny_app/all_dams.rds")

```


```{r shapefiles}

  path <- as.character(file_path %>% 
                     filter(country_name == "India") %>%
                     select(file_path))
  

mymap <- readOGR(path) 

mymap@data <- mymap@data %>% 
  clean_names()

all_dams <- read_rds("shiny_app/all_dams.rds")

all_dams_new <- all_dams %>%
  drop_na(decimal_degree_latitude) %>%
  filter(country == "India")  %>%
  group_by(nearest_city) %>%
  mutate(dams_count = n()) 

admin_list <- as.tibble(subnational %>%
  filter(country_name == "India") %>%
  select(admin_name, population) %>%
  rename(admin_new = admin_name))

tibble(name = mymap@data$admin_name, count = id_agg@data$dams_count) 

list <- as.tibble(id_agg@data$dams_count)

bind_cols(admin_list, list)
  

coordinates(all_dams_new) = c("decimal_degree_longitude","decimal_degree_latitude")
crs.geo1 = CRS("+proj=longlat")
proj4string(all_dams_new) = crs.geo1

id_agg = aggregate(x=all_dams_new["dams_count"],by = mymap, FUN = length)

qpal = colorBin("Reds", id_agg$dams_count, bins=4)

leaflet(id_agg) %>%
  addPolygons(stroke = TRUE,opacity = 1,fillOpacity = 0.5, smoothFactor = 0.5,
              color="black",fillColor = ~qpal(dams_count),weight = 1) %>%
  addLegend(values=~dams_count,pal=qpal,title="Dams") %>%
  addCircleMarkers(data = all_dams %>% drop_na(decimal_degree_latitude) %>% filter(country == "India"), lat = ~ decimal_degree_latitude, lng = ~ decimal_degree_longitude, radius = 0.1)

unique(subnational$country_name)
```
```{r make_choro}
make_choro <- function(file, country_name){
  country_dams <- all_dams %>%
    drop_na(decimal_degree_latitude) %>%
  filter(country == country_name)  
  
  admin_list <- as.tibble(subnational %>%
  filter(country_name == country_name) %>%
  select(admin_name, population) %>%
  rename(admin_new = admin_name) %>%
    mutate(count = c(1:nrow(.))))
  
  mymap <- readOGR(file)
  
  mymap@data <- mymap@data %>% 
  clean_names()

 mymap@data <- mymap@data %>%
  mutate(count = c(1:nrow(.))) %>%
  left_join(admin_list, by = "count") %>%
  mutate(admin_name = admin_new) %>%
  select(-admin_new, -count)

pal <- colorNumeric(palette = "viridis", domain = mymap@data$population, reverse = TRUE)
  
  leaflet(mymap) %>%
  addPolygons(stroke = TRUE,opacity = 1,fillOpacity = 0.5, smoothFactor = 0.5, weight = 1, fillColor = ~pal(population))   %>%
addLegend(values=~population,pal=pal,title="Population") %>%
  addCircleMarkers(data = country_dams, lat = ~ decimal_degree_latitude, lng = ~ decimal_degree_longitude, radius = 0.1)
}

path <- as.character(file_path %>% 
                     filter(country_name == country_name) %>%
                     select(file_path))

  mymap <- readOGR(path)

make_choro(path, "Zimbabwe")

country_dams <- all_dams %>%
    drop_na(decimal_degree_latitude) %>%
  filter(country == "Zimbabwe")  
  
  admin_list <- as.tibble(subnational %>%
  filter(country_name == "Zimbabwe") %>%
  select(admin_name, population) %>%
  rename(admin_new = admin_name) %>%
    mutate(count = c(1:nrow(.))))
  
  mymap <- readOGR("raw_data/subnational/geometry/zimbabwe/geo1_zw2012.shp")
  
  mymap@data <- mymap@data %>% 
  clean_names()

 mymap@data <- mymap@data %>%
  mutate(count = c(1:nrow(.))) %>%
  left_join(admin_list, by = "count") %>%
  mutate(admin_name = admin_new) %>%
  select(-admin_new, -count)

pal <- colorNumeric(palette = "viridis", domain = mymap@data$population, reverse = TRUE)
  
  leaflet(mymap) %>%
  addPolygons(stroke = TRUE,opacity = 1,fillOpacity = 0.5, smoothFactor = 0.5, weight = 1, fillColor = ~pal(population))   %>%
addLegend(values=~population,pal=pal,title="Population") %>%
  addCircleMarkers(data = country_dams, lat = ~ decimal_degree_latitude, lng = ~ decimal_degree_longitude, radius = 0.1)

make_choro("raw_data/subnational/geometry/zimbabwe/geo1_zw2012.shp", "Zimbabwe")




```


```{r read excel}
subnational <- read_excel("raw_data/subnational/clean_formatted_wb_subnational.xlsx")

mymap <- readOGR("raw_data/subnational/geometry/argentina/geo1_ar2010.shp") 

subnational

admin_list <- as.tibble(subnational %>%
  filter(country_name == "Argentina") %>%
  select(admin_name, population) %>%
  rename(admin_new = admin_name) %>%
    mutate(count = c(1:nrow(.))))

admin_list

mymap@data <- mymap@data %>%
  mutate(count = c(1:24)) %>%
left_join(admin_list, by = "count") %>%
  mutate(admin_name = admin_new) %>%
  select(-admin_new, -count)

ar_population <- subnational %>%
  filter(country_name == "Argentina")

mymap@data <- left_join(ar_population, mymap@data, by = "admin_name")

pal <- colorNumeric(
  palette = "viridis",
  domain = mymap@data$population,
  reverse = TRUE
)

qpal = colorBin("Reds", mymap@data$population, bins=10)


leaflet(mymap) %>%
  addPolygons(stroke = TRUE,opacity = 1,fillOpacity = 0.5, smoothFactor = 0.5, weight = 1, fillColor = ~pal(population))   %>%
addLegend(values=~population,pal=pal,title="Population") %>%
  addCircleMarkers(data = all_dams %>% filter(country == "Argentina") %>% drop_na(decimal_degree_latitude), lat = ~ decimal_degree_latitude, lng = ~ decimal_degree_longitude, radius = 0.1)
```
```{r nn}


leaflet() %>%
  addTiles() %>%
  addCircleMarkers(data = all_dams, lat = ~ decimal_degree_latitude, lng = ~ decimal_degree_longitude, radius = 0.1) %>%
  setView(lat = 0, lng = 0, zoom = 2)

basins <- readOGR("raw_data/basins/Major_Basins_of_the_World.shp")

gecon_v4 <- read_excel("raw_data/subnational/spatialecon-gecon-v4-xls/Original data/gecon-v4.xls", 
    sheet = "Sheet1") %>%
  clean_names() 

# use predict get predicted number of dams per population, covar country and lat/long

coordinates(gecon_v4) = c("longitude","lat")
crs.geo1 = CRS("+proj=longlat")
proj4string(gecon_v4) = crs.geo1
proj4string(gecon_v4) <- proj4string(basins)
grid_basins <- gIntersects(gecon_v4,basins,byid = TRUE)

basins@data$average_pop <- apply(grid_basins,1,function(x) mean(gecon_v4@data$popgpw_2005_40[x]))
basins@data$total_pop <- apply(grid_basins,1,function(x) sum(gecon_v4@data$popgpw_2005_40[x]))

qpal = colorBin(c("yellow", "red"), basins@data$total_pop, bins=10)
                
leaflet(basins) %>%
  addTiles() %>%
  addPolygons(stroke = TRUE,opacity = 0.5,fillOpacity = 0.5, smoothFactor = 0.5, weight = 1, fillColor = ~qpal(total_pop)) %>%
  addLegend(values=~total_pop,pal=qpal,title="Population") 
  #addCircleMarkers(data = all_dams %>%
   #                  drop_na(decimal_degree_latitude, decimal_degree_longitude), 
    #               lat = ~ decimal_degree_latitude, lng = ~ decimal_degree_longitude, radius = 0.1)
                ###
                
all_dams_new <- all_dams %>%
  group_by(major_basin) %>%
  mutate(dams_count = n()) %>%
  drop_na(decimal_degree_latitude) 

coordinates(all_dams_new) = c("decimal_degree_longitude","decimal_degree_latitude")
crs.geo1 = CRS("+proj=longlat")
proj4string(all_dams_new) = crs.geo1

basin_agg = aggregate(x=all_dams_new["dams_count"],by = basins, FUN = length)

qpal = colorBin("Reds", basin_agg$dams_count, bins=6)


leaflet(basin_agg) %>%
  addTiles() %>%
  addPolygons(stroke = TRUE,opacity = 0.5,fillOpacity = 0.5, smoothFactor = 0.5, weight = 1, fillColor = ~qpal(dams_count)) %>%
  addLegend(values=~dams_count,pal=qpal,title="Number of Dams and Reservoirs") %>% 
  addCircleMarkers(data = all_dams %>%
                     drop_na(decimal_degree_latitude, decimal_degree_longitude), 
                   lat = ~ decimal_degree_latitude, lng = ~ decimal_degree_longitude, radius = 0.1)


```
dams_map <- left_join(mymap, all_dams, by = "country") 
  

coordinates(gecon_v4) = c("longitude","lat")
crs.geo1 = CRS("+proj=longlat")
proj4string(gecon_v4) = crs.geo1

ar_agg = aggregate(x=gecon_v4["mer2005_40"],by=mymap, FUN = length)

qpal = colorBin("Reds", ar_agg$mer2005_40, bins=5)

leaflet(ar_agg) %>%
  addPolygons(stroke = TRUE,opacity = 1,fillOpacity = 0.5, smoothFactor = 0.01,
              color="black",fillColor = ~qpal(mer2005_40),weight = 0.1) %>%
  addLegend(values=~mer2005_40,pal=qpal,title="people") %>%
  addCircleMarkers(data = all_dams %>% filter(country == "Argentina"), lat = ~ decimal_degree_latitude, lng = ~ decimal_degree_longitude, radius = 0.1)

pal <- colorNumeric(palette = "YlGnBu", domain = gecon_v4$popgpw_2005_40)
  
leaflet() %>%
  addTiles() %>%
  addCircleMarkers(data = gecon_v4, lat = ~ lat, lng = ~ longitude, radius = 0.1, color = ~ pal(gecon_v4$popgpw_2005_40)) %>%
  setView(lat = -38.4161, lng = -63.6167, zoom = 4)
  
  